\cvsection{Work Experience}

\begin{cventries}

  \cventry
  {Graduate Student Researcher, advised by Prof.\,Edward A. Lee}
  {U.C. Berkeley, TerraSwarm Research Center}
  {Berkeley}
  {Aug. 2012 -- (expected) May. 2018}
  {
    \begin{cvitems}
      System research for mobile and Internet of Things (IoT) applications (see
      research projects for details).
    \end{cvitems}
  }

  \cventry
  {Software Engineer Intern, hosted by Dr.\,Roy Want, Dr.\,Bill Schilit}
  {Google Research}
  {Mountain View}
  {Jun. 2015 -- Aug. 2015}
  {
    \begin{cvitems}
      An exploration of using Android and Bluetooth LE to implement a
      wireless-sensor Data Mule system.
    \end{cvitems}
  }

  \cventry
  {Software Engineer Intern, hosted by Dr.\,Liang Jin}
  {Google, Search Infrastructure}
  {Mountain View}
  {May. 2014 -- Aug. 2014}
  {
    \begin{cvitems}
      Optimized wide-area crawling scheduling. Designed and implemented a global
      DNS sharding system based on target locality rather than hash
      partition. The system runs in production and has effectively reduced
      99-percentile latency and cross-datacenter traffic.
    \end{cvitems}
  }

  \cventry
  {Research Intern, mentored by Dr.\,Xiaofan Fred Jiang}
  {Microsoft Research Asia (MSRA)}
  {Beijing}
  {May. 2010 -- Mar. 2011}
  {
    \begin{cvitems}
      \item \textbf{LiveSynergy}. Evaluated various technologies (802.15.4, Bluetooth
      Low Energy, and RFID) on metrics like boundary sharpness, consistency,
      range, power consumption for indoor localization. Led the design and
      implementation of a magnetic-based proximity detection hardware platform.
      \item \textbf{SEPTIMU}. Designed the hardware platform (1cm by 1cm) which
      integrates 3-axis accelerometer, gyroscope, thermometer, photo-diode and
      microphone.
    \end{cvitems}
  }

\end{cventries}

%%% Local Variables:
%%% coding: utf-8
%%% mode: latex
%%% TeX-engine: xetex
%%% TeX-master: "../cv"
%%% End:
