\cvsection{Selected Publications}

\begin{cventries}

  \begin{cvitems}

  \item {\bf Ben Zhang}, Xin Jin, Sylvia Ratnasamy, John Wawrzynek, Edward
    A. Lee, ``AWStream: Adaptive Wide-Area Streaming Analytics,'' in
    SIGCOMM'2018. (acceptance rate: 18\%)

  \item David A. Mellis, {\bf Ben Zhang}, Audrey Leung, Bj\"orn Hartmann,
    ``Machine Learning for Makers: Interactive Sensor Data Classification Based
    on Augmented Code Examples,'' in Designing Interactive Systems
    (DIS'2017). (\textbf{Honorable Mention Award}, acceptance rate: 24\%)

  \item {\bf Ben Zhang}, Nitesh Mor, John Kolb, Douglas S. Chan, Nikhil Goyal,
    Ken Lutz, Eric Allman, John Wawrzynek, Edward A. Lee, and John Kubiatowicz,
    ``The Cloud is Not Enough: Saving IoT from the Cloud,'' in HotCloud
    2015. (acceptance rate: 30\%)

  \item {\bf Ben Zhang}, Yu-Hsiang Chen, Claire Tuna, Achal Dave, Yang Li,
    Edward A. Lee and Bj\"orn Hartmann, ``HOBS: Head Orientation-Based Selection
    in Physical Spaces,'' in Spatial User Interaction (SUI'14). (acceptance
    rate: 30\%)

  \item Shahriar Nirjon, Robert F. Dickerson, Qiang Li, Philip Asare, John
    A. Stankovic, Dezhi Hong, {\bf Ben Zhang}, Xiaofan Jiang, Guobin Shen, and
    Feng Zhao, ``MusicalHeart: A hearty way of listening to music,'' In SenSys
    2012. (acceptance rate: 19\%)

  \item {\bf Ben Zhang}, Kaifei Chen, Yun Cheng, Chieh-Jan Mike Liang, Xiaofan
    Jiang, and Feng Zhao, ``Location-log: Bringing Online Shopping Benefits to
    the Physical World with Magnetic-based Proximity Detection,'' in Mobile
    Sensing 2012.

  \item Xiaofan Jiang, Chieh-Jan Mike Liang, Kaifei Chen, {\bf Ben Zhang}, Jeff
    Hsu, Bin Cao, Jie Liu, and Feng Zhao, ``Design and Evaluation of a Wireless
    Magnetic-based Proximity Detection Platform for Indoor Applications,'' in
    IPSN 2012. (acceptance rate: 15\%)

  \item Xiaofan Jiang, Chieh-Jan Mike Liang, Kaifei Chen, {\bf Ben Zhang}, Jeff
    Hsu, Jie Liu, Feng Zhao, ``Demo: Creating Interactive Virtual Zones in
    Physical Space with Magnetic-Induction,'' in SenSys 2011. ({\bf Best Demo
      Award})

  \end{cvitems}
\end{cventries}

%%% Local Variables:
%%% coding: utf-8
%%% mode: latex
%%% TeX-engine: xetex
%%% TeX-master: "../cv"
%%% End:
