\cvsection{Research Projects}

\begin{cvskills}

  \cvskill {AWStream} {AWStream is a stream processing system for wide-area
    streaming analytics. It integrates application adaptation as a first-class
    programming abstraction and automatically learns an accurate profile that
    models accuracy and bandwidth trade-off. Using the profile, the runtime
    system simultaneously achieves low latency and high accuracy.}

  \\[-1em]
  
  \cvskill {ESP} {Example-based Sensor Prediction (ESP) system leverages
    expert-authored machine learning pipelines to drive an auto-generated
    interface that allows machine-learning novices to modify and adapt the
    pipelines for use in their own projects. ESP allows novices to visualize
    pipeline performance; manage training data; and configure pipeline
    parameters.}
  
  \\[-1em]

  \cvskill {GDP} {Global Data Plane (GDP) is a data-centric abstraction focused
    around the distribution, preservation, and protection of information. It
    offers the same application model as the cloud but better matches the needs
    and characteristics of the IoT by utilizing heterogeneous computing
    platforms, such as small gateway devices, moderately powerful nodes in the
    environment and the cloud, in a distributed manner.}

  \\[-1em]

  \cvskill {HOBS} {Head Orientation-Based Selection (HOBS) is a novel technique
    for interacting with smart devices at a distance. We augment a commercial
    wearable device, Google Glass, with an infrared (IR) emitter to select
    targets equipped with IR receivers, achieving ``what you see is what you can
    control.''}

\end{cvskills}

%%% Local Variables:
%%% coding: utf-8
%%% mode: latex
%%% TeX-engine: xetex
%%% TeX-master: "../cv"
%%% End:
